---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## hw09 : A package to assist in the visualization of linear model results

The goal of hw09 is to create an easy to use package that allows users to quickly visualize the objects produced in a simple linear model, including a table of regression coefficients and p values, as well as qplot using the lmfun() function. Please note, the pow function is a silly add on that was mostly developed in class.

The gapminder data were included as a readily accessible way for the user to practice using the function. I added to the pow function we developed in class to include plots but also to exploit some of the different test that expressions.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(hw09)
lmfun(gapminder$lifeExp, gapminder$gdpPercap, mydata = gapminder)

pow(1:35, 5)
```
