---
title: "Visualizing Linear Model Objects"
author: "Emily west"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package is not intended for general use, but rather to practice and manipulate the functionalities of packages.

The functions contained in this package assist the user in visualizing the output objects of simple linear regressions, specifically the regression coefficients, p-values and qplots. The gapminder dataset is included to provide the user with a dataset in which to experiment with the uses of the package.

There are many things that can be manipulated within a vignette, and I have chosen to keep some of the following examples as "cheat sheet" for my future self, although I have modified a few to discover for myself what is happening behind the scenes.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:25, xlab = "new label", ylab = "new label")
plot(10:1)
```

This figure caption is made possible by including `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
